The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-29 Writeup/paper_v3.tex
Removed s in referring to a single figure

\subsection{Other morphological parameters}
For other morphological parameters such as the \sersic index and \btt ratio, we do not compare the distributions themselves directly. 
For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be between 0.05 and 0.95. %\arun{What exactly do we do here?}.
We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.

In Figs.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 
that the mass selected sample doesn't include as many disk-like galaxies as in luminosity selected samples.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

>>>>

\subsection{Other morphological parameters}
For other morphological parameters such as the \sersic index and \btt ratio, we do not compare the distributions themselves directly. 
For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be between 0.05 and 0.95. %\arun{What exactly do we do here?}.
We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Fig.~\ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.

In Fig.~\ref{fig:median_sersicn}, we see that the \sersic indices of mass selected sample (\s$3$) are systematically greater than those of the luminosity selected samples (\s$1$,\s$2$).
This is consistent with the \btt values being higher in \s$3$ than in \s$1$ or \s$2$ in Fig.~\ref{fig:median_dvcbtt}. This is not just an edge effect but can be seen from the distributions themselves 
that the mass selected sample doesn't include as many disk-like galaxies as in luminosity selected samples.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}
